COG-ED Manuscript

### 2022-01-14 06_Paper/COG-ED/Manuscript.Rmd
finalized lowerplot for SCA

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign, color = predictor, group = predictor)) +
    geom_line() +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_continuous(position = "right") +
    ggtitle("Fixed effects estimate") +
    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1))

>>>>

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign, color = predictor, group = predictor)) +
    geom_line() +
    geom_text(aes(x = length(pipelines_data)-2, y = -0.01, label = "NFC")) + 
    geom_text(aes(x = length(pipelines_data)-2, y = -0.12, label = "Level")) +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_continuous(position = "right") +
    ggtitle("Fixed effects estimate") +
    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1), legend.position = "none")

  # add columns to the data frame that describe the pipeline

  sca_results$Dim <- ifelse(substr(sca_results$pipeline,1,2) == "AA", 2,
                            ifelse(substr(sca_results$pipeline,1,2) == "AW", 3,
                                   ifelse(substr(sca_results$pipeline,1,2) == "WW", 4,
                                          ifelse(substr(sca_results$pipeline,1,2) == "WA", 5, NA))))
  sca_results$Trans <- ifelse(substr(sca_results$pipeline,3,3) == "R", 7,
                              ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
                                     ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
                                            ifelse(substr(sca_results$pipeline,3,3) == "I", 9,
                                                   ifelse(substr(sca_results$pipeline,3,3) == "S", 10, NA)))))
  sca_results$Excl <- ifelse(substr(sca_results$pipeline,4,4) == "N", 12,
                             ifelse(substr(sca_results$pipeline,4,4) == "2", 13,
                                    ifelse(substr(sca_results$pipeline,4,4) == "5", 14,
                                           ifelse(substr(sca_results$pipeline,4,4) == "3", 15,
                                                  ifelse(substr(sca_results$pipeline,4,4) == "O", 16, 
                                                         ifelse(substr(sca_results$pipeline,4,4) == "T", 17, NA))))))

  # create the lower part of the plot that indicates the pipeline specifications

  sca_lowerplot <- ggplot(data = sca_results) +
    geom_hline(yintercept = c(1,6,11), color = "grey", size = 0.5) +
    geom_hline(yintercept = c(2:5,7:10,12:17), color = "grey", linetype = "dashed", size = 0.2) +
    geom_point(aes(x = num, y = Dim)) +
    geom_point(aes(x = num, y = Trans)) +
    geom_point(aes(x = num, y = Excl)) +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_reverse(breaks = c(1:17), lim = c(17,0), labels = c(expression(bold("Dimension")),
                                                                "Across S, across C", "Across S, within C",
                                                                "Within S, within C", "Within S, across C",
                                                                expression(bold("Transformation")),
                                                                "Raw/None", "Log", "Inverse", "Square-root",
                                                                expression(bold("Exclusion")),
                                                                "None", "2 MAD from median", "2.5 MAD from median",
                                                                "3 MAD from median", "100ms after onset", "200ms after onset")) +
    theme(axis.text.x = element_blank(), legend.position = "none")
